---
title: "05-Manual-Annotation"
author: "Hannah Nowers"
date: "2026-02-19"
output: pdf_document
---
## Creating Annotation Table for Dermasterias Proteins

```{bash}

head -2 ../data/uniprotkb_GO.tsv #Taking a look at my unirprot table

pwd

cd ..

pwd

head -n 5 data/derm-protein.fa # Taking a look at the first 5 rows of my protien seq


```

#Running my derm-protein query seq through the db
```{bash}

~/GitHub/Github-Practice/Data/ncbi-blast-2.17.0+/bin/blastp \
-query ../../seastar-capstone/data/derm-protein.fa \
-db ../../Github-Practice/blastdb/uniprot_sprot_r2023_01 \
-out ../../Seastar-capstone/output/derm_gene_blastx.tab \
-evalue 1E-20 \
-num_threads 8 \
-max_target_seqs 1 \
-outfmt 6

```

#Taking a look at my table and cleaning it
```{bash}

head -2 ../output/derm_gene_blastx.tab
wc -l ../output/derm_gene_blastx.tab

sed 's/|/\t/g' ../output/derm_gene_blastx.tab \
> ../output/derm-uniprot_blastx_sep.tab #first line: sed 's/|/\t/g'-> mean translate and replace every \ with a tab, Second line: > means put Ab_4-uniprot_blastx.tab through the translation, replacing | with tab and then making a new file Ab_4-uniprot_blastx_sep.tab

head -2 ../output/derm-uniprot_blastx_sep.tab

```
# Join Tables in R

```{r}

bltabl_derm_gene <- read.csv("../output/derm-uniprot_blastx_sep.tab", sep = '\t', header = FALSE) #blast table
spgo <- read.csv("../data/uniprotkb_GO.tsv", sep = '\t', header = TRUE) # annotation table

```

# Annotation Table Creation
```{r}

derm_annot <- left_join(bltabl_derm_gene, spgo,  by = c("V3" = "Entry")) %>%
select(V1, V3, V13, Protein.names, Organism, Gene.Ontology..biological.process.) 

```


## Annotation Table for Pisaster Protiens

#Checking my Data
```{bash}

pwd 
cd ..
head -n 5 data/pisaster-protein.fa # Taking a look at the first 5 rows of my protein seq


```

#Running my pisaster-protein query seq through the db
```{bash}

~/GitHub/Github-Practice/Data/ncbi-blast-2.17.0+/bin/blastp \
-query ../../seastar-capstone/data/pisaster-protein.fa \
-db ../../Github-Practice/blastdb/uniprot_sprot_r2023_01 \
-out ../../Seastar-capstone/output/pisaster_gene_blastx.tab \
-evalue 1E-20 \
-num_threads 8 \
-max_target_seqs 1 \
-outfmt 6

```


#Taking a look at my Pisaster table and cleaning it
```{bash}

head -2 ../output/pisaster_gene_blastx.tab
wc -l ../output/pisaster_gene_blastx.tab

sed 's/|/\t/g' ../output/pisaster_gene_blastx.tab \
> ../output/pisaster-uniprot_blastx_sep.tab #first line: sed 's/|/\t/g'-> mean translate and replace every \ with a tab, Second line: > means put Ab_4-uniprot_blastx.tab through the translation, replacing | with tab and then making a new file Ab_4-uniprot_blastx_sep.tab

head -2 ../output/pisaster-uniprot_blastx_sep.tab

```

# Join Tables in R

```{r}

bltabl_pisaster_gene <- read.csv("../output/pisaster-uniprot_blastx_sep.tab", sep = '\t', header = FALSE) #blast table
spgo <- read.csv("../data/uniprotkb_GO.tsv", sep = '\t', header = TRUE) # annotation table

```

# Annotation Table for Pisaster Creation
```{r}

pisaster_annot <- left_join(bltabl_pisaster_gene, spgo,  by = c("V3" = "Entry")) %>%
select(V1, V3, V13, Protein.names, Organism, Gene.Ontology..biological.process.) 

```


##Creating Annotation Table for Dermasterias Proteins
```{bash}

head -2 ../data/uniprotkb_GO.tsv #Taking a look at my unirprot table

pwd

cd ..

pwd

head -n 5 data/pycno-protein.fa # Taking a look at the first 5 rows of my protien seq


```

#Running pycno-protein query seq through the db
```{bash}

~/GitHub/Github-Practice/Data/ncbi-blast-2.17.0+/bin/blastp \
-query ../../seastar-capstone/data/pycno-protein.fa \
-db ../../Github-Practice/blastdb/uniprot_sprot_r2023_01 \
-out ../../Seastar-capstone/output/pycno_gene_blastx.tab \
-evalue 1E-20 \
-num_threads 8 \
-max_target_seqs 1 \
-outfmt 6

```

#Taking a look at my pycno table and cleaning it
```{bash}

head -2 ../output/pycno_gene_blastx.tab
wc -l ../output/pycno_gene_blastx.tab

sed 's/|/\t/g' ../output/pycno_gene_blastx.tab \
> ../output/pycno-uniprot_blastx_sep.tab #first line: sed 's/|/\t/g'-> mean translate and replace every \ with a tab, Second line: > means put Ab_4-uniprot_blastx.tab through the translation, replacing | with tab and then making a new file Ab_4-uniprot_blastx_sep.tab

head -2 ../output/pycno-uniprot_blastx_sep.tab

```


```{r}

bltabl_pycno_gene <- read.csv("../output/pycno-uniprot_blastx_sep.tab", sep = '\t', header = FALSE) #blast table
spgo <- read.csv("../data/uniprotkb_GO.tsv", sep = '\t', header = TRUE) # annotation table
```

# Annotation Table Creation
```{r}
pycno_annot <- left_join(bltabl_pycno_gene, spgo,  by = c("V3" = "Entry")) %>%
select(V1, V3, V13, Protein.names, Organism, Gene.Ontology..biological.process.) 

```


```{bash}

git push origin main


```